---
title: "Week 1 Tasks - Data Science Programming"
author: "[Your Name Here]"
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: true
    toc_float: true
    theme: united
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Week 1 Tasks

This R Markdown document contains solutions to all Week 1 tasks using the `student_scores.csv` dataset.

---

## Task 1 – Hello World

Write a program that prints: "Welcome to Data Science Programming!"

```{r task1}
# Task 1: Hello World
# Write your code here

```

---

## Task 2 – Simple Math

Calculate and print the result of:
- 15 + 23
- 120 / 6  
- 5³ (5 to the power of 3)

```{r task2}
# Task 2: Simple Math
# Write your code here

```

---

## Task 3 – Variables and Vectors

Create a vector of 5 numbers: `c(10, 20, 30, 40, 50)`.

Print the vector and the sum of its elements.

```{r task3}
# Task 3: Variables and Vectors
# Write your code here

```

---

## Task 4 – Plot Squares

Create a vector of numbers from 1 to 10.

Plot the numbers against their squares using the `plot()` function.

```{r task4}
# Task 4: Plot Squares
# Write your code here

```

---

## Task 5 – Load Dataset

Load `student_scores.csv` into your program.

Display the first 5 rows.

```{r task5}
# Task 5: Load Dataset
# Write your code here

```

---

## Task 6 – Summary Statistics

Print the average (mean) of the `Score` column.

Print the minimum and maximum scores.

```{r task6}
# Task 6: Summary Statistics
# Write your code here

```

---

## Task 7 – Filtering Data

Find and print the names of students who scored greater than 80.

```{r task7}
# Task 7: Filtering Data
# Write your code here

```

---

## Task 8 – Sorting Data

Sort the dataset by `Score` in descending order.

Display the top 3 students.

```{r task8}
# Task 8: Sorting Data
# Write your code here

```

---

## Task 9 – Visualization

Create a histogram of scores.

Add appropriate title and axis labels.

```{r task9}
# Task 9: Visualization
# Write your code here

```

---

## Submission Notes

- Ensure all code chunks run without errors
- Include appropriate comments in your code
- Make sure plots are properly displayed
- Knit this document to HTML/PDF before submission
- Save and submit this file as `Week1_Tasks.Rmd`

---

*End of Week 1 Tasks*
